From Education to Entrepreneurship

### 2014-12-03 index.Rmd
Added temp gvis hist
Added chart to troubleshoot

>>>>

```{r}
library(googleVis)

set.seed(123)
Dropped4=data.frame(A=rpois(100, 20),
             B=rpois(100, 5),
             C=rpois(100, 50))
print( 
  gvisHistogram(Dropped4, options=list(
    legend="{ position: 'top', maxLines: 2 }",
    colors="['#5C3292', '#1A8763', '#871B47']",
    width=600, gvis.plot.tag = 'chart'),
    chartid="Histogram")
)
```

```{r}
library(googleVis)

# Import CompleteData
C1 <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", stringsAsFactors = TRUE)

# Drop unecessary column in C1
C1$X <- NULL

C1$WayofTeach <- NULL
C1$PercentFear <- NULL
C1$PercentNascent <- NULL
C1$PercentOwner <- NULL
C1$PercentPerceived <- NULL
C1$PercentIntention <- NULL

# Change format of Year column
C1[,"Year"] <- as.factor(C1[,"Year"])

##### Can't get gsub to change date format
names(C1$Year) <- gsub("2001", "2001-01-01", names(C1$Year))

C2 <- as.Date(C1$Year, origin = "2001-01-01")

# Set value as numeric
C1[,"PercentOpportunities"] <- as.numeric(C1[,"PercentOpportunities"])

A1 <- gvisAnnotatedTimeLine(C1, datevar = "Year", numvar = "PerceivedOpportunities", idvar = "Country", 
    titlevar = "Title", annotationvar = "Annotation", options = list(displayAnnotations = TRUE, 
        legendPosition = "newRow", width = 600, height = 300), chartid = "ATL")

plot(A1)
```
